---
title: "Whole genome structural variation analysis using Nanopore long DNA sequence reads"
date: "Report created: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    number_sections: yes
    self_contained: yes
    theme: default
    highlight: null
    css: Static/ont_tutorial.css
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    df_print: paged
link-citations: yes
bibliography: Static/Bibliography.bib
always_allow_html: yes
---

<div style="position:absolute;top:0px;right:0px;padding:15px;background-color:gray;width:45%;">
```{r, echo=FALSE}
knitr::include_graphics("https://nanoporetech.com/themes/custom/nanopore/images/ont-logo.svg?tutorial=cas9enrichment")
```
</div>


```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy=TRUE, tidy.opts=list(width.cutoff=80), 
                      fig.width=9, fig.height=6, warning=FALSE, message=FALSE, 
                      kable.force.latex=TRUE,
                      highlight=TRUE,
                      cache.path="Analysis/Cache/",
                      knitr.table.format = "html",
                      width = 120,
                      knitr.kable.NA = '')

options(knitr.kable.NA = '')

library(yaml)
library(session)
library(kableExtra)
library(ggplot2)
library(RColorBrewer)
library(scales) # required for comma
library(reshape2)
library(dplyr)
library(xlsx)

config <- yaml.load_file("config.yml")
tutorialText   <- config$tutorialText


### here lie dragons ###
# expeditions below this comment at your own risk
# welcome feedback and suggestions ...

slurpContent <- function(filename) {
  include = as.logical(tutorialText)
  if (include) {
    paste(readLines(filename),collapse="\n")
  }
}

reportDPI <- 90
colMax <- 4

#knitr::knit_exit()
```


`r slurpContent("Static/TutorialPreamble.md")`

```{r, echo=FALSE}
r_results <- file.path("Analysis","R")
# if r_results does not exist the snakemake either failed or has not run -- flag a warning?
```




# Reproducible research - produce your own report

This report has been created using **`Rmarkdown`**, publicly available **`R`** packages, and the \LaTeX document typesetting software for reproducibility. For clarity the **`R`** packages used, and their versions, are listed below.

\fontsize{8}{12}

```{r sessionInfo, eval=TRUE, echo=FALSE, comment=NA}
utils:::print.sessionInfo(sessionInfo()[-7], locale=FALSE)
```

\fontsize{10}{14}

It is also worth recording the versions of the software that have been used for the analysis.

\fontsize{8}{12}

```{r, engine='bash', echo=FALSE, comment=NA}
conda list "samtools|minimap2|snakemake|rstudio"
```

\fontsize{10}{14}

`r slurpContent("Static/TutorialPostamble.md")`

\pagebreak


# References and citations
